### 2021-03-10 ch/2-related-work.tex
Add to literature review

@@

>>>>

\citet{kallus2018residual} is another more conceptual work.
They present an intuitive model for how sampling bias can enter a training set
and how it can be very hard to correct for it.
The paper refers to the process as \emph{systematic censoring},
but this is not meant to necessarily imply that this censoring was a conscious decision by some authority;
it can also be an unintended side effect of an enacted policy.
Systematic censoring can arise any time a screening process prevents observing the outcome for the screened-out samples.
For example, if, historically, a certain demographic group was screened out from receiving loans,
then it was not possible to observe default rates for this group;
and so any historical data on defaulting is useless for that demographic group.
Even if a bank wants to change their policy,
it is hard to correct for the bias in the training set because there is not good data to learn from.
This is a prime example of a ground-truth-centric bias problem.

@@

\citet{maity2020notradeoff} provide a similar analysis to \citet{blum2020recovering},
but consider more general dataset biases.
Just like \citet{blum2020recovering}, they explicitly reject a fairness-accuracy trade-off,
because they evaluate on a balanced test set.
(In the paper this is formulated in terms of the optimal Bayes classifier satisfying their notions of fairness on the test set.)
They show that the sampling bias (in the training set) that they consider,
can be overcome by enforcing an appropriately chosen risk-based notion of algorithmic fairness;
either a notion they term \emph{risk parity} (inspired by \ac{DP})
or \emph{conditional risk parity} (inspired by \ac{EOdds}).
